Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Changed 'mentioned' to 'discussed'
Don't need to capitalize 'depth-masking' in caption
Say 'approach' in visual artifact screenshot

Both approaches are based on the volume rendering method in \cite{Kruger03}, as
previously mentioned.  To render part of a volume, they first render the texture
coordinates of the back faces of that part to a texture.  Then the front faces
of that part are rendered with a shader that uses the previously-stored texture
coordinates to form a ray through the volume.  The ray then samples the volume
at regular intervals.

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot.png}
\caption{Screenshot of Depth-Masking approach.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot-3.png}
\caption{Screenshot of Boolean XOR with visual artifact.}
\label{boolean-xor-with-artifact}
\end{figure}

>>>>

Both approaches are based on the volume rendering method in \cite{Kruger03}, as
previously discussed.  To render part of a volume, they first render the texture
coordinates of the back faces of that part to a texture.  Then the front faces
of that part are rendered with a shader that uses the previously-stored texture
coordinates to form a ray through the volume.  The ray then samples the volume
at regular intervals.

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot.png}
\caption{Screenshot of depth-masking approach.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot-3.png}
\caption{Screenshot of Boolean XOR approach with visual artifact.}
\label{boolean-xor-with-artifact}
\end{figure}
